A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-11-10 paper/elsarticle/elsarticle-template.tex
paper

The hardware setup employed in the evaluation (cf.\ Figure \ref{fig:eval}(a)) comprised a Panasonic PT-RZ660BE projector (Panasonic Corporation, Japan) with a steerable mirror system---used in our experiments to point the projection to each of the 15 locations---manufactured by Dynamic Projection Institute (Dynamic Projection Institute, Austria) \cite{rupprecht2020information,Rupprecht2021}. The steerable mirror system was bundled with the MDC-X software for steering the mirror, loading imagery, and optionally carrying out manual keystone correction, such that each position and (warped) image can be registered as a preset. In addition, we used a Stereolabs Zed 2 stereo camera (Stereolabs Inc., France) as our `downwards-facing' camera, making use of only its left view. The floorspace used for our experiments measured dimensions of ca.\ 6~m~$\times$~4~m; the projector was mounted at approximately the center of this space, at a height of ca.\ 3.5 m. At this height, the pixel size (i.e., length or width of a pixel if projected to the scene plane) of the camera was ca.\ 3.5 mm.

@@

\begin{table}[ht]
\caption{Means and standard deviations (in units of centimeters and pixels, respectively) of deviations in measured lengths from 50 cm for top and bottom and from 21.25 cm for left and right, with respect to the 15 augmentations produced using our approach  for 15 respective target locations (intended augmentation dimensions 50~cm~$\times$~31.25~cm). Pixel size given the downward-facing camera's height above the ground plane was 3.5 mm; note that in no instance did mean and standard deviation exceed 1 pixel from the viewpoint of the camera.}
\label{table:length}
\centering
{\small
\begin{tabularx}{7.4cm}{r p{1cm} p{1cm} p{1cm} p{1cm}}
\toprule
  & Top & Bottom & Left & Right \\
\midrule
Mean {\tiny[cm]} & 0.03 & 0.07 & 0.09 & 0.06 \\
Stdev {\tiny[cm]} & 0.33 & 0.17 & 0.17 & 0.17 \\
\midrule
Mean {\tiny[px]} & 0.1 & 0.19 & 0.26 & 0.18 \\
Stdev {\tiny[px]} & 0.95 & 0.48 & 0.49 & 0.49 \\
\bottomrule
\end{tabularx}}
\end{table}

\begin{table}[ht]
\caption{Means and standard deviations of deviations in measured angles from $90^\circ{}$ with respect to the 15 augmentations produced using our approach for 15 respective target locations.}
\label{table:angle}
\centering
{\small
\begin{tabularx}{6.75cm}{r p{1.95cm} p{1.95cm}}
\toprule
  & Top Left & Bottom Right \\
\midrule
Mean {\tiny[deg]} & -0.03 & 0.0 \\
Stdev {\tiny[deg]} & 0.4 & 0.34 \\
\bottomrule
\end{tabularx}}
\end{table}

\paragraph{Our approach} We began by carrying out a calibration of the camera, acquiring 10 camera calibration images (cf.\ Section~\ref{sec:approach:geometry}) of a chessboard calibration pattern with $6~\times~4$ corners ($7~\times~5$ squares) and feeding the images as input to our camera calibration module. Separately, for each of the 15 target locations, we produced a projector calibration image (cf.\ again Section~\ref{sec:approach:geometry}) by projecting a $11~\times~4$ asymmetrical circle pattern image to the target location in question by directing the projection using the steerable mirror, placing a chessboard pattern beside the projected pattern, and acquiring the image using the `downwards-facing' camera. We then fed these images alongside the output of the camera calibration module to our projector calibration module. For each of the target locations, the target location was registered in the MDC-X software as a preset. The output of the projector calibration module is a homography per input projector calibration image (cf.\ Section~\ref{sec:approach:homography}). Next, we warped the image of the TU Wien logo to the respective target locations using the corresponding homography, using a third dedicated custom module responsible for warping an image according to a homography. These warped images were finally imported into the MDC-X software and associated with their respective target location presets (cf.\ Figure~\ref{fig:eval}(b)).

Tables~\ref{table:length} and \ref{table:angle} give the deviations in measured lengths and angles, respectively, from the intended quantities. Lengths were measured using a measuring tape for the top, bottom, left, and right sides of the augmentations; angles were measured using an angle gauge at the augmentations' top-left and bottom-right corners (the measuring tape and angle gauge are both visible in Figure~\ref{fig:eval}(b)). Note that if deviations in measured lengths are expressed in units of pixels of the `downwards-facing' camera, mean and standard deviation in no instance exceed 1 pixel. The total amount of time expended for carrying out all the above steps amounted to ca.\ 20 min, with ca.\ 2 min going to acquisition of the camera calibration images, and ca.\ 5 min going to that of projector calibration images. The remainder of the time was spent running our modules or working with the MDC-X software. Note that once the camera is calibrated, that calibration can be reused if the camera's intrinsics remain fixed, in particular if no change is made to the zoom factor or focus settings of the camera.

>>>>

The hardware setup employed in the evaluation (cf.\ Figure \ref{fig:eval}(a)) comprised a Panasonic PT-RZ660BE projector (Panasonic Corporation, Japan) with a steerable mirror system---used in our experiments to point the projection to each of the 15 locations---manufactured by Dynamic Projection Institute (Dynamic Projection Institute, Austria) \cite{rupprecht2020information,Rupprecht2021}. The steerable mirror system was bundled with the MDC-X software for steering the mirror, loading imagery, and optionally carrying out manual keystone correction, such that each position and (warped) image can be registered as a preset. In addition, we used a Stereolabs Zed 2 stereo camera (Stereolabs Inc., France) as our `downwards-facing' camera, making use of only its left view. The floorspace used for our experiments measured dimensions of ca.\ 6~m~$\times$~4~m; the projector and camera were mounted at approximately the center of this space, at a height of ca.\ 3.5 m. At this height, the pixel size (i.e., length or width of a pixel if projected to the scene plane) of the camera was ca.\ 3.5 mm.

\begin{table}[ht!]
\caption{Mean absolute error (MAE), minimum absolute error, and maximum absolute error in units of centimeters, with respect to the four sides (top, bottom, left, right) of the 15~augmentations produced using our approach for 15 target locations spread across the floorspace, respectively. Errors were computed against intended augmentation dimensions of 50~cm~$\times$~31.25~cm (i.e., 50~cm for top and bottom, 31.25~cm---rounded to 31.3~cm for the purposes of the computing the errors---for left and right).} %Note that absolute errors in no instance exceeded 1~cm for any side of any of the 15~augmentations.
\label{table:length}
\centering
{\small
\begin{tabularx}{7.4cm}{r p{1cm} p{1cm} p{1cm} p{1cm}}
\toprule
  & Top & Bottom & Left & Right \\
\midrule
MAE {\tiny[cm]} & 0.23 & 0.17 & 0.22 & 0.2 \\
Min AE {\tiny[cm]} & 0.0 & 0.0 & 0.0 & 0.0 \\
Max AE {\tiny[cm]} & 0.8 & 0.6 & 0.5 & 0.5 \\
\bottomrule
\end{tabularx}}
\end{table}

@@

\begin{table}[ht!]
\caption{Mean absolute error (MAE), minimum absolute error, and maximum absolute error in units of degrees, with respect to the top-left and bottom-right corners of the 15~augmentations produced using our approach for 15 target locations spread across the floorspace, respectively. Errors computed in terms of deviation from $90^\circ{}$.}
\label{table:angle}
\centering
{\small
\begin{tabularx}{6.75cm}{r p{1.95cm} p{1.95cm}}
\toprule
  & Top Left & Bottom Right \\
\midrule
MAE {\tiny[deg]} & 0.17 & 0.32 \\
Min AE {\tiny[deg]} & 0.0 & 0.0 \\
Max AE {\tiny[deg]} & 0.9 & 0.5 \\
\bottomrule
\end{tabularx}}
\end{table}

\paragraph{Our approach} We began by carrying out a calibration of the camera, acquiring 10~camera calibration images (cf.\ Section~\ref{sec:approach:geometry}) of a chessboard calibration pattern with $6~\times~4$ corners ($7~\times~5$ squares) and feeding the images as input to our camera calibration module. Separately, for each of the 15~target locations, we produced a projector calibration image (cf.\ again Section~\ref{sec:approach:geometry}) by projecting a $11~\times~4$ asymmetrical circle pattern image to the target location in question by directing the projection using the steerable mirror, placing a chessboard pattern beside the projected pattern, and acquiring the image using the `downwards-facing' camera. We then fed these images alongside the output of the camera calibration module to our projector calibration module. For each of the target locations, the target location was registered in the MDC-X software as a preset. The output of the projector calibration module is a homography per input projector calibration image (cf.\ Section~\ref{sec:approach:homography}). Next, we warped the image of the TU Wien logo to the respective target locations using the corresponding homography, using a third dedicated custom module responsible for warping an image according to a homography. These warped images were finally imported into the MDC-X software and associated with their respective target location presets (cf.\ Figure~\ref{fig:eval}(b)).

Tables~\ref{table:length} and \ref{table:angle} give the errors in measured lengths and angles, respectively, with respect to the intended quantities. Lengths were measured using a measuring tape for the top, bottom, left, and right sides of the 15~augmentations; angles were measured using an angle gauge at the 15~augmentations' top-left and bottom-right corners. Note that absolute errors in lengths in no instance exceeded 1~cm for any side of any of the 15~augmentations, or $1^\circ{}$ for any of the measured corners. The total amount of time expended for carrying out all the above steps amounted to ca.\ 20~min, with ca.\ 2 min going to acquisition of the camera calibration images, and ca.\ 5 min going to that of projector calibration images. The remainder of the time was spent running our modules or working with the MDC-X software. Note that once the camera is calibrated, that calibration can be reused if the camera's intrinsics remain fixed, in particular if no change is made to the zoom factor or focus settings of the camera.
